### 2019-02-27 soc.tex
update preamble documentation

% LANGUAGE %
%-========-%
\usepackage{luavlna}                            % auto non-breaking spaces
\AtBeginDocument{\singlechars{czech}{AaIiVvOoUuSsZzKk}}
\usepackage[czech]{babel}                       % use the czech language

@@

% BIBLIOGRAPHY %
%-============-%
\usepackage[backend=biber,
            style=iso-numeric,
            sortlocale=cs_CZ,
            autolang=other,
            bibencoding=UTF8]{biblatex}         % use BibLaTeX for references
\addbibresource{soc.bib}                        % reference file

\renewcommand*{\finentrypunct}{}                % don't end the reference with .
\renewcommand{\multinamedelim}{\addcomma\space} % use comma as delimeter
\renewcommand{\finalnamedelim}{\addspace a \space} % use a as final name delim
\renewbibmacro{in:}{}                           % don't use In:

\DeclareFieldFormat{labelnumberwidth}{[#1]}     % wrap refs in square brackets

% TABLES          %
% requires: float %
%-===============-%
\floatstyle{plaintop}                           % table caption on top
\restylefloat{table}                            % -||-
\usepackage{booktabs}                           % table formatting
\setlength\heavyrulewidth{0.25ex}

@@

% MISCELLANEOUS %
%-=============-%
\usepackage[font=footnotesize,
            labelfont=bf,
            figurename=Obr.,
            tablename=Tab.,
            belowskip=-12pt]{caption}           % captions

@@

\setmainfont{CMU Serif}                         % a font that suports bx sc

>>>>

% LANGUAGE %
%-========-%
\usepackage{luavlna}                            % auto non-breaking spaces
\AtBeginDocument{\singlechars{czech}{AaIiVvOoUuSsZzKk}} % chars not to break on
\usepackage[czech]{babel}                       % use the czech language

@@

% BIBLIOGRAPHY %
%-============-%
\usepackage[backend=biber,
            style=iso-numeric,                  % numeric ISO 690
            sortlocale=cs_CZ,
            autolang=other,
            bibencoding=UTF8]{biblatex}         % use BibLaTeX for references
\addbibresource{soc.bib}                        % references file

\renewcommand*{\finentrypunct}{}                % don't end references with dot
\renewcommand{\multinamedelim}{\addcomma\space} % use comma as name delimeter
\renewcommand{\finalnamedelim}{\addspace a \space} % use a as final name delim.
\renewbibmacro{in:}{}                           % don't use In:
\DeclareFieldFormat{labelnumberwidth}{[#1]}     % wrap ref nums in sqr brackets

% TABLES          %
% requires: float %
%-===============-%
\floatstyle{plaintop}                           % table caption on top
\restylefloat{table}                            % -||-
\usepackage{booktabs}                           % table formatting
\setlength\heavyrulewidth{0.2ex}                % top and bottomrule thickness

@@

% MISCELLANEOUS %
%-=============-%
\usepackage[font=footnotesize,                  % 10pt captions
            labelfont=bf,                       % bold captions
            figurename=Obr.,                    % picture captions are "Obr."
            tablename=Tab.,                     % table captions are "Tab."
            belowskip=-12pt]{caption}           % reduced below skip

@@

\setmainfont{CMU Serif}                         % font supporting bold smallcaps
